How to fix IR

### 2017-08-25 political-analysis-draft/draftPA.tex
editing plot scripts

We also examine the accuracy of the predictions made with each approach. Finally, we assess whether there is any substantive finding that emerges or indeed if any disappear once the interdependencies in the data are modeled.%%%Dont we want to talk more about performance here???? - MG

@@

\begin{table}[ht]
\centering
\begin{tabular}{rl cc}
  \hline
 & Model & AUC (ROC) & AUC(PR) \\ 
  \hline
\multirow{2}{*}{Reiter and Stam (2003)} & GLM & 0.92 & 0.08 \\ 
~  & AME & 0.96 &  0.15 \\ 
\multirow{2}{*}{McDonald (2004)} & GLM & &  \\ 
~  & AME & &  \\ 
\multirow{2}{*}{Rose (2004)} & GLM & &  \\ 
~  & AME & &  \\ 
\multirow{2}{*}{Weeks (2012)} & GLM & &  \\ 
~  & AME & &  \\ 
\multirow{2}{*}{Gibler (2017)} & GLM & &  \\ 
~  & AME & &  \\ 
   \hline
\end{tabular}
\end{table}

>>>>

We also examine the accuracy of the predictions made with each approach. Out of sample cross validation strategy.

% % % % % % % % % % % % % % % % % % 
By accounting for exogenous and network dependent patterns that give rise to conflict systems we are able to better account for the data generating process underlying relational data structures. To show that this is the case, we examine whether our approach achieves better predictive performance in an out of sample context than traditional dyadic models. To evaluate our model, we randomly divide the $\binom n 2 \times T$ data values into $k=30$ sets, letting $s_{ij,t}$ be the set to which pair $ij,t$ is assigned. Then for each $s \in \{1,\ldots,k\}$, we:

\begin{enumerate}
	\item estimate model parameters with $\{y_{ij,t}: s_{ij,t} \neq s\}$, the data not in set $s$,
	\item and predict $\{\hat{y}_{ij,t}: s_{ij,t} = s\}$ from these estimated parameters. 
\end{enumerate}

\noindent The result of this procedure is a set of sociomatrices $\bm \hat Y$, in which each entry $\hat y_{ij,t}$ is a predicted value obtained from using a subset of the data that does not include $y_{ij,t}$.

We set a number of benchmarks for comparison. First we compare the AME model to a GLM model using the same covariates to show the effect of accounting for network dependencies on predicting conflict. We supplement this with an alternative GLM that includes not just these covariates, but also a lagged dependent variable and a lagged reciprocity term. The lagged dependent variable is the equivalent of saying that conflict and peace are relatively likely to persist between dyads, while the inclusion of a lagged reciprocity term in a GLM framework is a simple way to account for retaliatory strikes.

We utilize three performance criterions to compare the models: Receiver Operator Characteristic (ROC) curves, Precision Recall (PR) curves, and separation plots. ROC curves look at the trade-off between true positive rates and false positive rates at different thresholds of classification. An issue with an ROC Curve when looking at conflict, is that it is relatively rare at the dyadic level: in most years only 3\% of possible dyads are in conflict with one another. If peace is common, even a poor model will have a very low False Positive Rate.

To better assess which models predict the presence of conflict, not just its absence, we look at PR Curves. These examine the trade-offs between the percentage of conflicts a model predicts, and the percentage of predicted conflicts which occur. Lastly, we examine separation plots \citep{greenhill:etal:2011}. These provide an intuitive visualization of the accuracy of our predictions by juxtaposing a line showing the predicted probability of conflict with whether conflict actually occurs for all cases (where the cases are sorted by the predicted probability and then colored to indicate the outcome). Here a perfect model would have all cases where conflict actually exists on the right with a predicted probability of $1$, and would predict $0$ in all other cases. All of the models' performance out of sample by these metrics are displayed in figure \ref{fig:roc_ame}. The AME model with covariates is the best performing model out of sample in all cases. This model outperforms each of the GLM variants by a notable margin.
% % % % % % % % % % % % % % % % % %

Finally, we assess whether there is any substantive finding that emerges or indeed if any disappear once the interdependencies in the data are modeled.%%%Dont we want to talk more about performance here???? - MG

@@

\begin{table}[ht]
\centering
\begin{tabular}{rl cc}
  \hline
 & Model & AUC (ROC) & AUC(PR) \\ 
  \hline
\multirow{2}{*}{Reiter and Stam (2003)} & GLM & 0.92 & 0.08 \\ 
~  & AME & 0.96 &  0.15 \\ 
\multirow{2}{*}{McDonald (2004)} & GLM & &  \\ 
~  & AME & &  \\ 
\multirow{2}{*}{Rose (2004)} & GLM & &  \\ 
~  & AME & &  \\ 
\multirow{2}{*}{Weeks (2012)} & GLM & 0.64 & 0.004  \\ 
~  & AME & 0.97 &  0.15 \\ 
\multirow{2}{*}{Gibler (2017)} & GLM & &  \\ 
~  & AME & &  \\ 
   \hline
\end{tabular}
\end{table}
